Structuring College Access

### 2025-02-19 index.qmd
make maps fullscreen

      writeLines(str_c('<iframe data-src="', rq1_map, '" src="about:blank" width=100% height=100% allowtransparency="true"></iframe>'))

@@

      writeLines(str_c('<iframe data-src="./results/maps/rq2_map_', str_replace_all(m, " ", "_"), '.html" src="about:blank" width=100% height=100% allowtransparency="true"></iframe>'))

>>>>

      writeLines(str_c('<iframe data-src="', rq1_map, '" src="about:blank" width=100% height=100% allowtransparency="true"></iframe>'))
      writeLines('<p class="fullscreen">Fullscreen</p>')

@@

      writeLines(str_c('<iframe data-src="./results/maps/rq2_map_', str_replace_all(m, " ", "_"), '.html" src="about:blank" width=100% height=100% allowtransparency="true"></iframe>'))
      writeLines('<p class="fullscreen">Fullscreen</p>')
